### 2016-08-12 Engine.tex
添加:node split 部分(未完成)

Similar to the ``path compression'' technique widely used in trie-like
structures, the nodes in a path of AMT, each of which has only one
key, can be merged into one node. This technique can improve both time
and space efficiency of AMT. To illustrate this, consider the pattern
set $P=\{p_1=e^6u^5sscc,\; p_2=e^6u^5,\; p_3=e^6\}$ and its
corresponding AMT constructed by Algorithm 1. As shown in Fig (a), the
built AMT has three nodes, and each contains only one key. In a
typical x86\_64 architecture, this implementation of AMT roughly takes
55 bytes of memory: 15 bytes for the keys, 16 bytes for the child
pointers and 24 bytes for the pointers to the matching
functions. However, if we combine the three keys into one string,
these three nodes can be merged into one node (Fig (b)), as a result,
the child pointers are no longer needed and the number of function
pointers is reduced from three to one. The merged node is another type
of tree node in addition to the types we have introduced in Section
\ref{subsec:nodes}.

For the merged node, the only problem is how to distinguish among the
keys after they are concatenated, to address this issues, a
\emph{length array} is used to store the length of each key, where
each array element takes only one byte (using the \emph{unsigned char}
type). Through the length of each key, we can split the original keys
out, and searching the target string in the merged node can be
trivial.

In general, after node merging, the AMT contains only one merged node
which takes 26 bytes (15 bytes for the keys, 3 bytes for the length
array, and 8 bytes for the matching function pointer), thus, 29 bytes
are saved comparing with the original AMT. In addition, only one
random access to the memory is needed to get the merged node (the
original AMT needs three random memory accesses to get all its nodes),
thus, the cache can be fully used to improve the performance.

>>>>

Similar to the ``path compression'' technique that is widely used in
many trie-like structures, the nodes in a path of AMT, each of which
has only one key, can be merged into one node. This technique can
improve both time and space efficiency of AMT. To illustrate its
benefits, consider the pattern set
$P=\{p_1=e^6u^5sscc,\; p_2=e^6u^5,\; p_3=e^6\}$ and the corresponding
AMT constructed by Algorithm 1. As shown in Fig (a), the built AMT has
three nodes, and each contains only one key. In a typical x86\_64
architecture, this implementation of AMT roughly takes 55 bytes of
memory: 15 bytes for the three keys, 16 bytes for the two child
pointers and 24 bytes for the three pointers to the matching
functions. However, if we combine the three keys into one string,
these three nodes can be merged into one node (Fig (b)), as a result,
the child pointers are no longer needed and the number of function
pointers is reduced from three to one. The merged node is another type
of tree node in addition to the node types we have introduced in
Section \ref{subsec:nodes}.

For the merged node, the only problem is how to distinguish among the
keys after they are concatenated, to address this issues, a
\emph{length array} is used to store the length of each key, where
each array element takes only one byte (using the \emph{unsigned char}
type). Through the length of each key, we can delimit each original
keys, and thus, searching the target string in the merged node can be
trivial.

In general, after node merging, the AMT contains just one merged node
which only takes 26 bytes (15 bytes for the keys, 3 bytes for the
length array, and 8 bytes for the matching function pointer), thus, 29
bytes are saved comparing with the original AMT. In addition, only one
random access to the memory is needed to get the merged node (the
original AMT needs three random memory accesses to get all its nodes),
thus, the cache miss is reduced and the performance is improved.

\subsubsection{Node splitting}
\label{sec:node split}

Once the keys in a node share a common prefix, that prefix can be
removed from the keys and form a new single key node (since the prefix
is either a character or a string, the type of the new node is either
Map 4 or String Array). This technique can reduce a lot of redundant
comparisons while searching a target key in that node. For instance,
consider the node in Fig whose four keys share a common prefix $a^4$,
and a target key which is $a^4u$. it will be compared with the four
keys in order and finally takes $5 \times 4 = 20$ byte comparisons to
determine the inexistence of target key. However, if $a^4$ is split
out and form another new node as shown in Fig , for the same target,
only 8 byte comparisons (4 comparisons for $node_1$ and another 4
comparisons for $node_2$) is needed.
